Maintenance planning on French military aircraft operations

### 2018-06-01 R/roadef_presentation/roadef_presentation.Rmd
added dassault ppt, heuristic documentation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('scripts/params.R')
source('scripts/import_results.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
setwd("../")
source('functions/params.R')
source('functions/import_results.R')
exp_directory = PATHS[['experiments']] %>% paste0('201802141539/')
gantt <- print_solution(exp_directory, max_resources = 30)
show_gantt <- knitr::opts_knit$get("rmarkdown.pandoc.to")=="slidy"
```
